A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-30 paper.tex
Work in progress
Minor stetic updates

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet$ Last Gen.:] The generation that found the solution.
    \item[$\bullet$ Eval.:] The total number of evaluations the algorithm executed. 
    \item[$\bullet$ Time (sec):] Total elapsed or wall clock time, in seconds. 
    \item[$\bullet$ Eval/sec:] The calculated rate of evaluations per second.
\end{description}

>>>>

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet $Last Gen.] is the generation that found the solution.
    \item[$\bullet $Eval.] is the total number of evaluations the algorithm executed. 
    \item[$\bullet $Time (sec)] is the total elapsed or wall clock time, in seconds. 
    \item[$\bullet $Eval/sec] is the calculated rate of evaluations per second.
\end{description}
